### 2020-03-11 tex/intro.tex

\section{Introduction}
\label{intro}
NuCypher KMS~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral  scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
a ciphertext encrypted under Alice's public key into a ciphertext under the delegatee's, or Bob's,  
public key. This enables the latter to decrypt the data without revealing anything about the 
encryption keys or the raw data to the intermediate servers.

@@

Alice joins the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe curing which Bob is authorized to access Alice's data.  Furthermore, 
Alice will lock an amount of Ether into the policy to be used to pay Ursula for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All what she needs is an Ethereum 
wallet, being aware of the NuCypher network architecture to select Ursulas, and knowing the 
NuCypher rules of preparing access control policies.

@@

\subsection{Monetary Incentives in the NuCypher KMS Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy or data 
owner Alice, while the second is an inflation rewards, i.e., newly minted 
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, much similar to other cryptocurrencies out there.

@@

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's rewards suffers from two 
main problems: 
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation is agnostic to the number of 
requests Ursula serves. Thus an active Ursula who may serve a huge number of 
requests, and an idle one who does not receive any requests (or a 
malicious Ursula that does not answer the requests she receives from Bob), will 
both collect the same rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline, not answering any Bob, and be online just to call the confirm activity 
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
\end{itemize}

>>>>

\section{Introduction}
\label{intro}
The NuCypher network ~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral  scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
a ciphertext encrypted under Alice's public key into a ciphertext decryptable by the delegatee's, or Bob's,  
public key. This enables the latter to decrypt the data without revealing anything about the 
decryption keys or the raw data to the intermediate servers.

@@

Alice joins the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe curing which Bob is authorized to access Alice's data.  Furthermore, 
Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All what she needs is an Ethereum 
wallet, being aware of the NuCypher network architecture to select Ursulas, and knowing the 
NuCypher rules of preparing access control policies.

@@

\subsection{Monetary Incentives in the NuCypher Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy or data 
owner Alice, while the second is an inflation rewards, i.e., newly minted 
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, much similar to other cryptocurrencies out there.

@@

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's rewards suffers from two 
main problems: 
\david{It's important to clarify here if we're talking about inflation rewards, service fees, or both.}
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation is agnostic to the number of 
requests Ursula serves. Thus an active Ursula who may serve a huge number of 
requests, and an idle one who does not receive any requests (or a 
malicious Ursula that does not answer the requests she receives from Bob), will 
both collect the same rewards if they hold identical policies.
\david{We should make a distinction between being idle because there are no requests or being off-line. The former is a legitimate situation driven by factors outside Ursula's control, while the latter is a punishable action.}
\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline, not answering any Bob, and be online just to call the confirm activity 
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
\end{itemize}

### 2020-03-11 tex/solutions.tex

@@

To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
This can be done by having the policy contract select at random (like based 
on the block hash or any other mechanism) the leaf IDs to be opened. If 
Ursula fails to open them correctly within a predefined timeframe, she loses the 
whole feed she was supposed to collect for serving $\omega$ requests.

>>>>

\david{I think it is possible to aggregate current Umbral proofs. I started to explore this option in the past but there was no use for it at that moment.}

@@

To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
This can be done by having the policy contract select at random (like based 
on the block hash or any other mechanism) the leaf IDs to be opened. If 
Ursula fails to open them correctly within a predefined timeframe, she loses the 
whole fee she was supposed to collect for serving $\omega$ requests.
